%------------------------------------------------------------------------------
%	SECTION TITLE
%------------------------------------------------------------------------------

\cvsection{Experience}

%------------------------------------------------------------------------------
%	SECTION CONTENT
%------------------------------------------------------------------------------

\begin{cventries}

% ------------------------------------------------------------------------------

\cventry
{Data Science Fellow}
{SharpestMinds}
{Toronto, Ontario, CA}
{Aug. 2019 - Present}
{
\begin{cvitems}
% ------------------------    
\item {Synthesized data to allow retailers to make predictions on
    purchases by combining individual and aggregated socioeconomic data.}
\item {Built segregation models using Gaussian Copula in order to downscale
    aggregated data to individual level.}
\item {Applied Dense Neural Network (DNN) to combine multiple correlated
    datasets.}
\item {Currently measuring the quality of synthetic data and its performance on
    machine learning models.}
\end{cvitems}
}
%------------------------------------------------------------------------------

\cventry
{Postdoctoral Researcher}
{Massachusetts Institute of Technology}
{Cambridge, Massachusetts, US}
{Jun. 2017 - Jul. 2019}
{
\begin{cvitems}
%------------------------    
% \item {Studied bimetallic catalysts and matched experimental observations to
%     theoretical models using statistical simulations.}
\item {Developed an in-house python library for modeling and visualizing
    research data on bimetallic catalysts.}
\item {Automated data analysis processes using Shell, SQL, and Python scripts to
    reduce human error and improve result reproducibility.}
\item {Increased model accuracy for Au coverage by 22\% by identifying the
    integral of the signal counts as the most predictive feature.}
% \item {Presented research results to general as well as expert audiences
%     through seminars, conferences, talks, and posters.}
\end{cvitems}
}

%------------------------------------------------------------------------------

\cventry
{Research Assistant}
{University of Utah}
{Salt Lake City, Utah, US}
{Aug. 2011 - May. 2017}
{
\begin{cvitems}
% \item {Analyzed catalytic property of size-selected platinum clusters through  
%     large datasets generated from a custom surface science apparatus.}
\item {Increased data processing efficiency by converting old Excel spreadsheets
    to Jupyter Notebooks.}
\item {Made major contribution to the development of in-house software, which is used
    for data acquisition and system control.}
\item {Developed a novel technique to extract information from spectroscopic
    data that leads to uncovering unknown nano-particle size effect.}
% \item {Collaborated with 7 other research institutes for design and fabrication
%     of a sophisticated ultra-high vacuum instrument.}
\end{cvitems}
}

%------------------------------------------------------------------------------

\end{cventries}