%------------------------------------------------------------------------------
%	SECTION TITLE
%------------------------------------------------------------------------------

\cvsection{Projects}

%------------------------------------------------------------------------------
%	SECTION CONTENT
%------------------------------------------------------------------------------

\begin{cventries}

% ------------------------------------------------------------------------------

\cventry
{Source Code: https://github.com/superyang713/Synthetic\_Data\_Generation}
{Synthetic Data Generation}
{}
{}
{
\begin{cvitems}
\item {A framework to generate synthetic individual level data from
    multiple sources at different granularity levels.}
\item {Applied Gaussian copula model to correctly capture dependencies and
    marginal distributions of sampled survey data.}
\item {The resulting synthetic data can be used to extract insights beyond what
    is possible or practical through a federal census.}
\end{cvitems}
}

%------------------------------------------------------------------------------

\cventry
{Source Code: https://github.com/superyang713/LabCode}
{Research Data Analysis Toolkit}
{}
{}
{
\begin{cvitems}
\item {Open source python library for preprocessing, modeling, and visualizing
    research data collected from custom surface science instruments.}
\item {Developed algorithms to calculate surface coverage of Gold Nickel Alloy.}
\end{cvitems}
}

% ------------------------------------------------------------------------------

\cventry
{Demo: www.yangdaitech.com   Source Code: https://github.com/superyang713/ETL}
{Full Stack Web App Development}
{}
{}
{
\begin{cvitems}
\item {Identified a potentially profitable niche in the education market and
    decided to make a web app for English teaching and learning.}
\item {With limited budget, adopted AWS serverless technology as the most
    suitable backend.}
\item {Self-learned ReactJS framework and various Javascript modules for
    front-end development.}
\end{cvitems}
}

% ------------------------------------------------------------------------------

\end{cventries}


